Komols Complexity, Coresets, and Sketches in Machine Learning

### 2019-01-02 komlos.tex
citation

\begin{lemma} \label{lem:komlos anl}
Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion. The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq 1$, is bounded by
\[
K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}\right)
\]
For general $\|q\| \leq R$ we get
\[
K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)}\right)
\]
\end{lemma}
\begin{proof}
The proof follows from combining the above.
$$
\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \cdot \|q\|^k
$$
By Lemma \ref{uc} we can find signs $\sigma$ such that 
$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above the lemma follows.
\end{proof}

@@

\begin{theorem}
Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq \sqrt{R}$, has Komlos complexity of $O(\sqrt{d}/m)$. 
\end{theorem}
\begin{proof}
By transforming $x$ to $\tilde{x} = (x, \|x\|^2, 1)$ and $q$ to $\tilde{q} = (-2q, 1, \|q\|^2)$ we get $\ip{\tilde{x},\tilde{q}} = \|x-q\|^2$. Moreover, $\|q\| \le \sqrt{R}$ gives $\|\tilde q\| \le R$. The result follows from applying Theorem~\ref{analitic1} to $f(\ip{ \tilde q, \tilde x}) = f(\|q-x\|^2)$ apply for functions of $\|q-x\|^2$.
\end{proof}

@@

\section{Linear Regression}

@@

\noindent The last inequality is a direct application of the following Theorem.
\begin{theorem}\label{BansalInDaHouz}
For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i X_i||_{2} \le O(\sqrt{d_1 + d_2})$.
\end{theorem}
\begin{proof}
First, recount Banaszczyk's theorem. 
Let $\mathcal K$ be a convex body in $\R^d$ with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is i.i.d.\ Gaussian).
Let $x_1,\ldots,x_n$ be vectors in $\R^d$ with $\|x_i\| \le 1$. 
Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some universal constant $C$.

>>>>

\begin{lemma} \label{lem:komlos anl}
Let $f$ be a function of $\langle x,q\rangle$ such that $f(\langle x,q\rangle) = \sum_k \alpha_k \langle x,q\rangle^k$ is its Taylor expansion. The Komlos Complexity of the Family of functions $f_q(x) = f(\ip{q,x})$, indexed by $\|q\| \leq 1$, is bounded by
\[
K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k|\sqrt{k\log^3(k)}\right)
\]
For general $\|q\| \leq R$ we get
\[
K_m = \min_\sigma \sum_i \sigma_i f(x_i,q) =O\left( \sqrt{d} \sum_k  |\alpha_k| R^k \sqrt{ k\log^3(k)}\right)
\]
\end{lemma}
\begin{proof}
The proof follows from combining the above.
$$
\sum_i \sigma_i f(x_i,q) = \sum_k \alpha_k \sum_i \sigma_i \langle x_i,q\rangle^k =  \sum_k \alpha_k  \langle  \sum_i \sigma_i x_i^{\otimes k},q^{\otimes k}\rangle \le \sum_k |\alpha_k| \cdot \| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \cdot \|q\|^k
$$
By Lemma \ref{uc} we can find signs $\sigma$ such that 
$\| \sum_i \sigma_i x_i^{\otimes k}\|_{T_k} \le c\sqrt{d k \log^3(k)}$. Substituting into the above, the lemma follows.
\end{proof}

@@

\begin{theorem}
Let $f:\R\rightarrow\R$ be analytic. There exist a radius $R$ such that the function family of functions $f_q(x) = f(\|x-q\|^2)$, indexed by $\|q\| \leq \sqrt{R}$, has Komlos complexity of $O(\sqrt{d}/m)$. 
\end{theorem}
\begin{proof}
By transforming $x$ to $\tilde{x} = (1, x, \|x\|^2)$ and $q$ to $\tilde{q} = (\|q\|^2, -2q, 1)$ we get $\ip{\tilde{x},\tilde{q}} = \|q-x\|^2$. Moreover, $\|q\| \le \sqrt{R}$ gives $\|\tilde q\| \le R$. The result follows from applying Theorem~\ref{analitic1} to $f(\ip{ \tilde q, \tilde x}) = f(\|q-x\|^2)$.
\end{proof}

@@

%\section{Linear Regression}

@@

\noindent The last inequality is a direct application of the following Theorem.
\begin{theorem}\label{BansalInDaHouz}
For any set of matrices $X_1,...,X_n$ in $\R^{d_1 \times d_2}$ such that $\|X_i\|_{F} \le 1$ there exists a set of signs $s_1,...,s_n$ such that $||\sum_i \sigma_i X_i||_{2} \le O(\sqrt{d_1 + d_2})$.
\end{theorem}
\begin{proof}
First, recount Banaszczyk's Theorem~\cite{Banaszczyk}.
Let $\mathcal K$ be a convex body in $\R^d$ with Gaussian measure at least 1/2 ($\Pr[g \in \mathcal K] \ge 1/2$ where $g$ is i.i.d.\ Gaussian).
Let $x_1,\ldots,x_n$ be vectors in $\R^d$ with $\|x_i\| \le 1$. 
Then, there exist signs $\sigma_i$ such that $\sum \sigma_i x_i \in C \mathcal K$ for some universal constant $C$.
